\Title

### 2020-01-23 manuscript/manuscript.tex
Continue writing manuscript

Lets consider a set of gravity acceleration measurements $g_z$ on points
$\{\mathbf{p}_1, \ldots, \mathbf{p}_N\}$ and a set of point sources with mass
$\{m_1, \ldots, m_M\}$ located on points
$\{\mathbf{q}_1, \ldots, \mathbf{q}_M\}$.
The point sources must generate the same gravity field as the one measured:

@@

\noindent where $\rho(\mathbf{q})$ is the density distribution of a certain
physical-property evaluated on the point $\mathbf{q}$. This density
distribution can be approximated by a finite and discrete set of point sources
located on $\{\mathbf{q}_1, \ldots, \mathbf{q}_M\}$:

@@

\begin{equation}
    V(\mathbf{p})
    \simeq
    \sum\limits_{j=1}^{M} \frac{c_j}{|\mathbf{p} - \mathbf{q}_j|}.
\end{equation}

@@

Worth noting that solving equation~\ref{eq:linear-problem} is equivalent to
an inversion and thus solving an ill-posed problem by nature due to the
non-uniqueness and the instability of the possible solutions.
Therefore is usually needed to add regularization functions in order to obtain
stable solutions \citep{oliveira2013}.
Moreover there's no limitation on the amount of point sources.
The number of sources can either be equal, less or more than the number of
observation points, leading to well, under or overdetermined linear problem,
respectively.

Add other possible applications to the EQL like RTP or upward continuation.

EQL implementation on Harmonica.

>>>>

A classical approach for applying the equivalent sources technique would be to
propose a set of point sources that generate the same harmonic field that has
been measured.
This requires
Lets consider a set of gravity acceleration measurements $g_z$ on points
$\{\mathbf{p}_1, \ldots, \mathbf{p}_N\}$ and a set of point sources with mass
$\{m_1, \ldots, m_M\}$ located on points
$\{\mathbf{q}_1, \ldots, \mathbf{q}_M\}$.
The point sources must generate the same gravity field as the one measured:

@@

\noindent where $\rho(\mathbf{q})$ is the density distribution of a certain
physical-property evaluated on the point $\mathbf{q}$. Following
\citet{dampney1969}, this density distribution can be approximated by a finite
and discrete set of point sources located on $\{\mathbf{q}_1, \ldots,
\mathbf{q}_M\}$:

@@

\begin{equation}
    V(\mathbf{p})
    =
    \sum\limits_{j=1}^{M} \frac{c_j}{|\mathbf{p} - \mathbf{q}_j|}.
    \label{eq:eql-field}
\end{equation}

@@

By solving equation~\ref{eq:linear-problem} we can obtain the values of
$\mathbf{c}$ that better reproduce the measured field.
Then they can be used to predict the value of the harmonic field on any other
point where no measurement has been taken by evaluating
equation~\ref{eq:eql-field}.

Worth noting that solving equations~\ref{eq:linear-problem-g}
and~\ref{eq:linear-problem} is equivalent to performing an inversion and thus
solving an ill-posed problem by nature due to the non-uniqueness and the
instability of the possible solutions.
Therefore is usually needed to add regularization functions in order to obtain
stable solutions \citep{oliveira2013}.
Moreover there's no limitation on the amount of point sources.
The number of sources can either be equal, less or more than the number of
observation points, leading to well, under or overdetermined linear problem,
respectively.

% Add other possible applications to the EQL like RTP or upward continuation.

% EQL implementation on Harmonica.
